Almost compatible functions and infinite length games

### 2015-11-24 articles/almost-compatible-functions-and-topological-games/article.tex
S'(omega_2) but not S(omega_2) under CH

@@

  \begin{proof}
    This is actually a corollary of an observation of Todorcevic communicated
    by Dow in [TODO cite Gen Prog in Top I]:
    if every Kurepa family of size at most \(\theta\)
    extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
    So the result follows as
    every Kurepa family \(\mc K\) of size \(\omega\) extends to
    the cofinal Kurepa family \([\bigcup\mc K]^\omega\).

    We may alternatively
    obtain the result from the previous topological argument by using the family
    \(\mc K\) of compact sets in the constructed topology on
    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable. Thus \(\mc K\)
    is cofinal in \([\omega_k]^\omega\)
    since for every countable set \(A\), \(\cl A\) is compact and countable.
    It is Kurepa since for every countable set \(A\), let (TODO)
  \end{proof}

  \begin{corollary}
    \(S'(\omega_k)\) holds for all \(k<\omega\).
  \end{corollary}

>>>>

  \begin{proof}
    We use the family \(\mc K\) which is a base of \(\aleph_0\)-many compact
    open sets for each point in the constructed topology on
    \(\omega_n\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable, and the closure of every
    countable set is a compact countable set. Thus \(\mc K\)
    is cofinal in \([\omega_n]^\omega\).
    It is Kurepa since for every countable set \(A\), there are only countably
    many compact open sets in \(\mc K\)
    joined to \(A\) by a finite linked chain.
  \end{proof}

  This is alternatively a corollary of an observation of Todorcevic
  communicated by Dow in \cite{MR1229125}:
  if every Kurepa family of size at most \(\theta\)
  extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
  So the result follows as
  every Kurepa family \(\mc K\) of size \(\omega\) extends to
  the cofinal Kurepa family \([\bigcup\mc K]^\omega\).

  So we have our desired result.

  \begin{corollary}
    \(S'(\omega_n)\) holds for all \(n<\omega\). Under \(CH\), we have
    both \(S'(\omega_2)\) and \(\neg S(\omega_2)\).
  \end{corollary}

@@
